%-----------------------------------------------------------------------------------------------------------------------------------------------%
%	The MIT License (MIT)
%
%	Copyright (c) 2021 Jitin Nair
%
%	Permission is hereby granted, free of charge, to any person obtaining a copy
%	of this software and associated documentation files (the "Software"), to deal
%	in the Software without restriction, including without limitation the rights
%	to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%	copies of the Software, and to permit persons to whom the Software is
%	furnished to do so, subject to the following conditions:
%	
%	THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%	IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%	FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%	AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%	LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%	OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN
%	THE SOFTWARE.
%	
%
%-----------------------------------------------------------------------------------------------------------------------------------------------%

%----------------------------------------------------------------------------------------
%	DOCUMENT DEFINITION
%----------------------------------------------------------------------------------------

% article class because we want to fully customize the page and not use a cv template
\documentclass[a4paper,12pt]{article}

%----------------------------------------------------------------------------------------
%	FONT
%----------------------------------------------------------------------------------------

% % fontspec allows you to use TTF/OTF fonts directly
% \usepackage{fontspec}
% \defaultfontfeatures{Ligatures=TeX}

% % modified for ShareLaTeX use
% \setmainfont[
% SmallCapsFont = Fontin-SmallCaps.otf,
% BoldFont = Fontin-Bold.otf,
% ItalicFont = Fontin-Italic.otf
% ]
% {Fontin.otf}

%----------------------------------------------------------------------------------------
%	PACKAGES
%----------------------------------------------------------------------------------------
\usepackage{url}
\usepackage{parskip} 	

%other packages for formatting
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}

%tabularx environment
\usepackage{tabularx}

%for lists within experience section
\usepackage{enumitem}

% centered version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X} 

%to prevent spillover of tabular into next pages
\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.47\textwidth}

%custom \section
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}

%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}

%for publications
\usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}

%Setup hyperref package, and colours for links
\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
\addbibresource{citations.bib}
\setlength\bibitemsep{1em}

%for social icons
\usepackage{fontawesome5}

%debug page outer frames
%\usepackage{showframe}


% job listing environments
\newenvironment{jobshort}[2]
    {
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \hfill &  #2 \\[3.75pt]
    \end{tabularx}
    }
    {
    }

\newenvironment{joblong}[2]
    {
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \hfill &  #2 \\[3.75pt]
    \end{tabularx}
    \begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt,label=--]
    }
    {
    \end{itemize}
    \end{minipage}    
    }



%----------------------------------------------------------------------------------------
%	BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}

% non-numbered pages
\pagestyle{empty} 

%----------------------------------------------------------------------------------------
%	TITLE
%----------------------------------------------------------------------------------------

% \begin{tabularx}{\linewidth}{ @{}X X@{} }
% \huge{Your Name}\vspace{2pt} & \hfill \emoji{incoming-envelope} email@email.com \\
% \raisebox{-0.05\height}\faGithub\ username \ | \
% \raisebox{-0.00\height}\faLinkedin\ username \ | \ \raisebox{-0.05\height}\faGlobe \ mysite.com  & \hfill \emoji{calling} number
% \end{tabularx}

\begin{tabularx}{\linewidth}{@{} C @{}}
\Huge{Davide Baldelli} \\[7.5pt]
\href{https://github.com/Dundalia}{\raisebox{-0.05\height}\faGithub\ Dundalia} \ $|$ \ 
\href{https://www.linkedin.com/in/davide-baldelli-b55618203/}{\raisebox{-0.05\height}\faLinkedin\ davide-baldelli-b55618203} \ $|$ \ 
\href{https://dundalia.github.io}{\raisebox{-0.05\height}\faGlobe \ dundalia.github.io} \ $|$ \ 
\href{mailto:davide.baldelli@mila.quebec}{\raisebox{-0.05\height}\faEnvelope \ davide.baldelli@mila.quebec} 
\end{tabularx}

%Interests/ Keywords/ Summary
\section{Summary}

PhD Student at MILA and Polytechnique Montréal.

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\section{Education}
\begin{tabularx}{\linewidth}{@{}l X@{}} 	
Jan 2025 - Current & PhD in Computer Engineering \hfill \normalsize (GPA: 4.0) \\
& \normalsize at \textbf{MILA and Polytechnique Montréal} \\
 & \normalsize Supervisors: Sarath Chandar, Amal Zouaq \\

Sept 2021 - Oct 2023 & MSc in Artificial Intelligence \hfill \normalsize (110/110 cum laude) \\
& \normalsize at \textbf{University of Bologna} \\

Sept 2017 - Mar 2021 & BSc in Mathematics \hfill \normalsize (110/110) \\
& \normalsize at \textbf{University of Florence} \\

Sept 2012 - June 2017 & Scientific High School \hfill \normalsize (96/100) \\
& \normalsize at \textbf{Liceo Scientifico Guido Castelnuovo} \\
\end{tabularx}
 
%----------------------------------------------------------------------------------------
% EXPERIENCE SECTIONS
%----------------------------------------------------------------------------------------


%Experience
\section{Work Experience}

\begin{joblong}{Freelance Machine Learning Engineer, Upwork}{June 2024 - Jan 2025}
\item Delivered a variety of machine learning projects for international clients, consistently earning 5-star ratings for quality, speed, and communication.
\end{joblong}

\begin{joblong}{Machine Learning Engineer, Loop AI Group}{Sept 2023 - Dec 2024}
\item {
        Co-supervised a master's thesis titled \href{https://thesis.unipd.it/handle/20.500.12608/70905}{\underline{"Self Assessment Tool for Medical Exam Candidates"}} in collaboration with the University of Padova.
Guided the candidate in applying machine learning techniques to develop a self-assessment tool.
Assisted in research direction, methodology selection, and technical problem-solving.
        }
\item Conducted deep learning project for musical Deepfake detection algorithm achieving 94\% of F1 score on a proprietary italian deepfake music dataset.
\item Conducted deep learning project for automatic translation of audio data for content creation.
\item Implemented statistical and deep learning based time series analysis models to solve demand forecasting.
\item Implemented BERT-based email classifier tool for an italian University's administrative office, achieving 98\% accuracy.
\end{joblong}

\begin{joblong}{Data Scientist Consultant, Loop AI Group}{Sept 2022 - Sept 2023}
\item Implemented closed-domain generative question-answering systems on technical topics, exploiting SoTA Pretrained Seq2Seq \\Language Models.
\item Implemented rule-based and transformers-based text retrievers.
\end{joblong}
  
%----------------------------------------------------------------------------------------
%\t RESEARCH EXPERIENCE
%----------------------------------------------------------------------------------------
\section{Research Experience}

\begin{joblong}{Research Intern (MSc Thesis), National Institute of Informatics — Tokyo, Japan}{Mar 2023 - Aug 2023}
\item Advisors: Akiko Aizawa, Junfeng Jiang, Paolo Torroni
\item Title: A TWO-step LLM Augmented distillation method for passage Reranking (\href{https://amslaurea.unibo.it/30082/}{MSc Thesis})
\item Conducted research in Text Information Retrieval, investigating open-source LLMs, text retrievers, rerankers, knowledge distillation, and ranking losses. Adapted a T5 model for reranking using GPT-augmented labels, achieving state-of-the-art results on TREC-DL and BEIR.
\end{joblong}

\begin{joblong}{BSc Thesis, University of Florence — Florence, Italy}{Sept 2020 - Mar 2021}
\item Advisor: Francesca Romana Nardi
\item Title (translated): Big Deviations for Markov Chains (\href{https://github.com/Freddavide/Freddavide/blob/main/elaborato_B036_Baldelli_Davide.pdf}{PDF})
\item Presented a theorem on the asymptotic behavior of Markov chains for rare events analysis within large deviations theory.
\end{joblong}
  
%----------------------------------------------------------------------------------------
%	 PROJECTS
%----------------------------------------------------------------------------------------

% \section{Projects}

% \begin{tabularx}{\linewidth}{ @{}l r@{} }
% \textbf{Some Project} & \hfill \href{https://some-link.com}{Link to Demo} \\[3.75pt]
% \multicolumn{2}{@{}X@{}}{long long line of blah blah that will wrap when the table fills the column width long long line of blah blah that will wrap when the table fills the column width long long line of blah blah that will wrap when the table fills the column width long long line of blah blah that will wrap when the table fills the column width}  \\
% \end{tabularx}

%----------------------------------------------------------------------------------------
%	 ACHIEVEMENTS
%----------------------------------------------------------------------------------------
\section{Achievements}
\begin{tabularx}{\linewidth}{@{}l X@{}}
Jun 2025 & Selected Participant, Y Combinator AI Startup School — San Francisco, CA \\
Jun 2022 & 4th place, Loop Q Prize Competition — Italy \\
\end{tabularx}

%----------------------------------------------------------------------------------------
%	 CERTIFICATIONS
%----------------------------------------------------------------------------------------
\section{Certifications}
\begin{tabularx}{\linewidth}{@{}l X@{}}
Apr 2025 & Agents Course, Hugging Face — Remote \\
\end{tabularx}

%----------------------------------------------------------------------------------------
%	PUBLICATIONS
%----------------------------------------------------------------------------------------
\section{Publications}
\begin{refsection}[citations.bib]
\nocite{*}
\printbibliography[heading=none]
\end{refsection}

%----------------------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------------------
\section{Skills}
\begin{tabularx}{\linewidth}{@{}l X@{}}
Programming &  \normalsize{Python (fluent); HTML, CSS, R, MatLab, Minizinc, NetLogo (familiar).}\\
Data Science  &  \normalsize{Numpy, Pandas, Scikit-learn, Matplotlib, Seaborn, Plotly}\\  
Deep Learning  &  \normalsize{Pytorch, Pytorch-lightning, Tensorflow.}\\  
NLP  &  \normalsize{HuggingFace, Transformers, Prompt Engineer, OpenAI GPT.}\\  
Web Development  &  \normalsize{Flask, Webflow}\\  
Miscellaneous  &  \normalsize{Linux, Shell, \LaTeX (Overleaf/R Markdown), Git, Docker, Figma, Blender.}\\  
Soft Skills  &  \normalsize{Time Management, Teamwork, Problem-solving, Documentation, Engaging Presentation.}\\  
\end{tabularx}

%----------------------------------------------------------------------------------------
%\t MISCELLANEOUS / LEADERSHIP
%----------------------------------------------------------------------------------------
\section{Leadership \& Community Involvement}

\begin{joblong}{\shortstack[l]{Leadership in Non-Profit Organization,\\ Belle Parole Arci APS -- Florence, Italy}}{Nov 2023 - Present}
\item Involved in founding and leading Belle Parole Arci APS, a non-profit organization.
\item Responsible for organizing community events and managing bar operations as part of the organization's activities.
\item Emphasized community engagement, cultural enrichment, and team coordination in a non-profit setting.
\item Built the website of the organization: \href{http://belleparoleaps.it}{\textbf{belleparoleaps.it}}.
\end{joblong}

%----------------------------------------------------------------------------------------
%\t LANGUAGES
%----------------------------------------------------------------------------------------
\section{Languages}
\begin{tabularx}{\linewidth}{@{}l X@{}}
English &  \normalsize{Professional proficiency}\\
Italian  &  \normalsize{Native proficiency}\\  
\end{tabularx}

\vfill
\center{\footnotesize Last updated: \today}

\end{document}
