%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Professional Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
    \cventry
    {Teaching Assistant - Summer High School Internships} % Job title
    {MILA} % Organisation
    {Montréal, Canada} % Location
    {Summer 2025} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and delivered educational workshops on Machine Learning and Probability for high school students.}
      \end{cvitems}
    }
    
    \cventry
    {Freelance Machine Learning Engineer} % Job title
    {Independent Consultant (Upwork Platform)} % Organisation
    {Remote} % Location
    {June 2024 - Jan 2025} % Date(s) - Use a range that covers all projects
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Delivered a variety of machine learning projects for international clients, consistently earning 5-star ratings for quality and speed.}
      \end{cvitems}
    }

    \cventry
    {Machine Learning Engineer} % Job title
    {Loop AI Labs Inc.} % Organisation
    {Remote} % Location
    {Sept 2022 - Dec 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {
        Co-supervised a master's thesis titled \href{https://thesis.unipd.it/handle/20.500.12608/70905}{"Self Assessment Tool for Medical Exam Candidates"} in collaboration with the University of Padova.
        }
        \item {Conducted project on Musical Deepfake Detection achieving 94\% of F1 score on a proprietary dataset.}
        \item {Implemented BERT-based email classifier for an italian University's administration, achieving 98\% accuracy.}
      \end{cvitems}
    } 

    
    \begin{comment}
    
    \cventry
    {Machine Learning Engineer and Master's Thesis Co-Supervisor} % Job title
    {Loop AI Group} % Organisation
    {Full Time - Fully Remote} % Location
    {Sept 2023 - Dec 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {
        Co-supervised a master's thesis titled \href{https://thesis.unipd.it/handle/20.500.12608/70905}{"Self Assessment Tool for Medical Exam Candidates"} in collaboration with the University of Padova.
        }
        \item {Conducted project on Musical Deepfake Detection achieving 94\% of F1 score on a proprietary dataset.}
        % \item {Conducted deep learning project for automatic translation of audio data for content creation.}
        % \item {Implemented statistical and deep learning based time series analysis models to solve demand forecasting.}
        \item {Implemented BERT-based email classifier for an italian University's administration, achieving 98\% accuracy.}
      \end{cvitems}
    }

    
    \cventry
    {Data Scientist Consultant} % Job title
    {Loop AI Group} % Organisation
    {Part Time - Fully Remote} % Location
    {Sept 2022 - Sept 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implemented closed-domain generative QA systems on technical topics, exploiting Pretrained Seq2Seq Language Models.}
        \item {Implemented rule-based and transformers-based text retrievers.}
      \end{cvitems}
    } 
    \cventry
    {Bartender} % Job title
    {Chiosco il Tempio} % Organisation
    {Part Time - Florence, Italy} % Location
    {June 2017 - Sept 2022} % Date(s)
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Managed inventory and organized events, improving customer engagement and operational efficiency.}
        \item {Led team scheduling and ensured high standards of service and compliance with safety regulations.}
        \item {\textbf{Soft Skills:} Public Relations Management, Communication, Time Management, Multitasking.}
    \end{cvitems}
    }
    \end{comment}


\end{cventries}
