%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Education}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
 
 \begin{comment}
 \cventry
    {PhD in Computer Engineering} % Degree
    {MILA and Polytechnique Montreal} % Institution
    {Montreal, Canada} % Location
    {Aug 2024 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {\textbf{Supervised by:} Sarath Chandar and Anbil Parthipan.}
      \end{cvitems}
    }
    \end{comment}
 
    \cventry
    {PhD in Computer Engineering} % Degree
    {MILA and Polytechnique Montréal} % Institution
    {Montréal, Canada} % Location
    {Jan 2025 - Current} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item  {GPA: 4.0}
        \item {\textbf{Supervisors:} Sarath Chandar, Amal Zouaq.}
        \item {\textbf{Courses:} Representation Learning, Reinforcement Learning.}
      \end{cvitems}
    }
    
    \cventry
    {MSc in Artificial Intelligence} % Degree
    {University of Bologna} % Institution
    {Bologna, Italy} % Location
    {Sept 2021 - Oct 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item  {Grade: 110/110 cum laude.}
        \item {\textbf{Courses:} Programming for Data Science, Knowledge Representation and Reasoning, Statistical Theory and Methods, Machine Learning, Deep Learning, Computer Vision, Natural Language Processing.}
      \end{cvitems}
    }
    
  \cventry
    {BSc in Mathematics} % Degree
    {University of Florence} % Institution
    {Florence, Italy} % Location
    {Sept 2017 - Mar 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Grade: 110/110.}
        \item {\textbf{Courses:} Mathematical Analysis, Linear Algebra, Group Theory, Geometry, Probability and Statistics, Logic and Computability.}
      \end{cvitems}
    }
    
  \cventry
    {Scientific High School} % Degree
    {Liceo Scientifico Guido Castelnuovo} % Institution
    {Florence, Italy} % Location
    {Sept 2012 - June 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Passed with 96/100.}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
